TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2018-08-14 paper/draft.tex
move paragraph

@@

\thecannon\ model can in principle be trained on any physical or empirical labels available. However, limitations to consider are that test labels from \thecannon\ are only accurate if the training labels accurate, and only precise if the training labels are measured using a consistent method. \thecannon\ does not extrapolate well outside the parameter space of the training sample.
\color{gcolor}{HOGG: More notes to add here?}\color{black}

>>>>

\thecannon\ model can in principle be trained on any physical or empirical labels available, giving a wide range of flexibility to the model, however choosing a training sample with high quality (accurate and precise) is critical to the performance of \thecannon. Limitations to consider are that test labels from \thecannon\ are only accurate if the training labels accurate, and only precise if the training labels are measured using a consistent method. Also choosing a sample with large dynamic range spanning the entire parameter space of interest is important, as \thecannon\ does not extrapolate well outside the parameter space of the training sample.
\color{gcolor}{HOGG: More notes to add here?}\color{black}

@@
